FraCaS: Temporal Analysis

### 2020-10-01 paper2020/paper.tex
deal with reviewer 2 and 3

\paragraph{Temporal Semantics}
\todo{Fold this in some other section}
In this paper we borrow several notions from classical temporal
semantics such as ``stative'', ``achievement'', ``activity'', etc.,
even though our definitions do not perfectly match the classical
ones. We explain our precise meaning for these terms in the body of the
paper. Nevertheless, we refer the reader to \citet{steedman:2000} for
an extensive review of formal temporal semantics.

@@

@@

@@

Thanks to the unicity of action of $write(smith,x,...)$ we find
\([t_1,t_2] = [t_3,t_4]\), and due to the years 1991 and 1992 being
disjoint we obtain contradiction.

@@

  Of particular note is the use of the pronoun ``it'', and the fact
  that adverbials expressions such that ``in 1992'' are lexicalized.
  We also follow the GF convention to postfix lexical items with the
  name of their category.

@@

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type-theoretical_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.

@@

We have presented a first attempt for a computational approach dealing
with the temporal section of the FraCaS test suite. To do this, we
have provided a new, simplified taxonomy of aspectual classes for verb
phrases, guided by the applicability of the unicity of action and
temporal subsumption properties.

>>>>

@@

\paragraph{Aside: aspectual classes in the literature}
In this paper we borrow several notions from classical temporal
semantics such as ``stative'', ``achievement'', ``activity'', etc.,
even though our definitions do not perfectly match the classical
ones. We explain our precise meaning for these terms in the body of the
paper. Nevertheless, we refer the reader to \citet{steedman:2000} for
an extensive review of formal temporal semantics.

@@

Unicity of action plays the role of event coreference in
(neo-)davidsonian account \todo{citation}. It is also a fine-grained
principle, allowing coreference to take into account certain arguments
when referencing. As we detail below, taking arguments into account
yields is critical to handle repeatability of achievements.

@@

Thanks to the unicity of action of $write(smith,x,...)$ (the subject
and direct object are fixed) we find \([t_1,t_2] = [t_3,t_4]\), and
due to the years 1991 and 1992 being disjoint we obtain contradiction.

@@

Of particular note is the use of the pronoun ``it'', and the fact that
adverbials expressions such that ``in 1992'' are lexicalized.  We also
follow the GF convention to postfix lexical items with the name of
their category. Most of the other categories follow usual naming
conventions. We remind the reader that ``slash'' categories are used
to swap the order of arguments (compared to non-slashed categories of
similar names).

@@

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.

@@

We have presented a first attempt for a computational approach dealing
with the temporal section of the FraCaS test suite. To do this, we
have provided a new, simplified taxonomy of aspectual classes for verb
phrases, guided by the applicability of the unicity of action and
temporal subsumption properties. While part of this simplification is
accidental (conflation of activity and accomplishment), we find that
other parts (the automatic distinction between repeatable and
unrepeatable achievements) constitute theoretical improvements.
